%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

\colorlet{awesome}{awesome-skyblue}


% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{profile}
\name{Varun}{Mathur}


\mobile{(+1) 4376625443}
\email{v3mathur@uwaterloo.ca}
\homepage{www.posquit0.com}
\github{posquit0}
\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient{Dayforce}{Canada}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Developer Intern}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
Having cultivated a deep-rooted passion for software development, I am thrilled to express my interest in the Dayforce Software Developer Intern position. Currently pursuing my Bachelor of Computer Science at the University of Waterloo, I am an avid learner eager to immerse myself in real-world challenges. My academic journey has furnished me with a robust understanding of modern programming languages such as **Python, JavaScript, and C++**, complemented by practical application through various projects and internships.

At the heart of my enthusiasm lies a self-starter spirit, evidenced in my internship experiences where I engineered automated systems across different platforms. At Alaan, I crafted a Python automation leveraging OpenAI APIs to streamline data extraction — a project that bolstered accuracy by **30%** and resulted in significant cost savings. This blend of creativity, technical skills, and a problem-solving mindset positions me as a unique asset in any collaborative setting, allowing me to contribute effectively to team goals.

\lettersection{Why Dayforce?}
The commitment to fostering a **high-performance culture** with opportunities for mentorship and growth resonates deeply with my aspirations. Dayforce's emphasis on innovation and customer focus aligns perfectly with my values, inspiring me to be part of a team that strives to elevate human capital management solutions. At Dayforce, I envision collaborating with seasoned professionals while diving into real-world projects that leverage technologies such as **Docker, Kubernetes, and Selenium** –- areas I am particularly excited to develop expertise in. The prospect of contributing to a company renowned for its cutting-edge solutions in human capital management motivates me immensely, as I aim to participate actively in its evolutionary strides.

\lettersection{Why Me?}
Coupling my **proficiency in software development** with an intense drive for continuous improvement makes me an ideal candidate for the Dayforce team. My background in projects like developing a decision forest regression model for air quality predictions and automating pipelines for data cleaning underscores my technical dexterity and innovative acumen. These projects refined my understanding of **CI/CD processes, data management, and algorithmic thinking**, all pivotal to advancing Dayforce's initiatives.

Furthermore, my adeptness in teamwork, demonstrated through successful collaborations in both academic and professional settings, ensures seamless integration into cross-functional teams. My project management experience using a diversity of tools, such as **Azure DevOps and Git**, is an asset that will complement Dayforce's operational practices, facilitating a cohesive workflow. With an unwavering work ethic and a passion for tech-driven problem solving, I am poised to significantly contribute to crafting solutions that elevate employee and customer experiences alike. 

In conclusion, I am eager to bring my skills and background to Dayforce, ready to learn and grow in an environment that values creativity and excellence in the ever-evolving field of software development.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
