%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

\colorlet{awesome}{awesome-skyblue}


% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{profile}
\name{}{Varun Mathur}


\mobile{(+1) 4376625443}
\email{v3mathur@uwaterloo.ca}
\github{varunmathur2005}
\linkedin{varunmathur2005}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient{Geotab}{Waterloo, Ontario - Canada}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Developer Intern}
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
{\today}
{Varun Mathur~~~·~~~Cover Letter}
{}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
As a third-year Bachelor of Computer Science candidate at the University of Waterloo, I have honed my expertise in **object-oriented design** and cloud technologies through a series of impactful internships in software development. My experiences have equipped me with a robust technical skill set in languages such as Python, TypeScript, and SQL, and in frameworks including React.js and Node.js. Additionally, I have contributed to innovative projects that emphasize automation and AI-driven solutions, aligning with modern industry needs.

\lettersection{Why Geotab?}
Geotab's commitment to **innovation**, customer success, and sustainability strongly resonates with my career aspirations and personal values. I am particularly inspired by Geotab’s drive to enhance technological systems for better client experiences, closely aligning with my own experience in developing and improving software solutions. Geotab’s focus on **sustainability** is pivotal for the tech industry's future, and I am eager to contribute to projects that support this mission.

\lettersection{Why Me?}
My background in **cloud systems** and **automation**, especially my recent work deploying CI/CD pipelines and automating data processing with AWS Lambda, directly supports Geotab's technological landscape. The roles I have held, such as my tenure at Alaan where I collaborated with DevOps to streamline deployments, showcase my **self-starter** and **adaptive** nature. I am experienced in working collaboratively, having succeeded in cross-functional teams to improve software interfaces and functionalities, similar to your initiatives with MyGeotab. I am enthusiastic about leveraging my passion for **learning new technologies** and my strong foundation in **communication** and **teamwork** to thrive in this dynamic environment.

\textbf{This cover letter is generated using Knock Knock, a project by Varun Mathur.}

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
