%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for Cover Letter
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Authors:
% Claud D. Park <posquit0.bj@gmail.com>
% Lars Richter <mail@ayeks.de>
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

\colorlet{awesome}{awesome-skyblue}


% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[circle,noedge,left]{profile}
\name{Varun}{Mathur}


\mobile{(+1) 4376625443}
\email{v3mathur@uwaterloo.ca}
\homepage{www.posquit0.com}
\github{posquit0}
\linkedin{posquit0}
% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \twitter{@twit}
% \skype{skype-id}
% \reddit{reddit-id}
% \medium{madium-id}
% \googlescholar{googlescholar-id}{name-to-display}
%% \firstname and \lastname will be used
% \googlescholar{googlescholar-id}{}
% \extrainfo{extra informations}


%-------------------------------------------------------------------------------
%	LETTER INFORMATION
%	All of the below lines must be filled out
%-------------------------------------------------------------------------------
% The company being applied to
\recipient{Stripe}{Canada}
% The date on the letter, default is the date of compilation
\letterdate{\today}
% The title of the letter
\lettertitle{Job Application for Software Engineer, Data Processing Infra }
% How the letter is opened
\letteropening{Dear Hiring Manager,}
% How the letter is closed
\letterclosing{Sincerely,}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Claud D. Park~~~·~~~Cover Letter}
  {}

% Print the title with above letter informations
\makelettertitle

%-------------------------------------------------------------------------------
%	LETTER CONTENT
%-------------------------------------------------------------------------------
\begin{cvletter}

\lettersection{About Me}
I am a dynamic and innovative software engineer with a deep-seated passion for creating robust, reliable, and scalable computing infrastructure. Currently pursuing a Bachelor of Computer Science at the University of Waterloo, I have cultivated a broad skill set, with proficiency in programming languages such as Python, JavaScript, C++, and SQL, paired with hands-on experience in technologies like React.js, Node.js, Microsoft Azure, and Apache Spark. My academic and professional journey has been driven by curiosity and a desire to tackle complex challenges, further honed by internships that emphasize automation, state management, and user engagement.

\lettersection{Why Stripe?}
Stripe's unwavering commitment to operational excellence and its global influence on the economy resonate strongly with my career aspirations. The company's emphasis on open-source contributions not only parallels my professional values but also presents an opportunity to be part of a forward-thinking team that shapes the future of financial infrastructure. Stripe's mission-driven culture, combined with its pioneering approach to data processing infrastructure, provides an inspiring environment for technologists keen on making meaningful impacts at a global scale. The prospect of contributing to Stripe's trajectory of innovation excites me.

\lettersection{Why Me?}
My robust experience in leading technical projects, coupled with a mastery of distributed systems and data processing tools such as Spark, Flink, and Kafka, make me a perfect fit for Stripe's engineering team. As demonstrated in my previous roles at Alaan (YC W23) and SpeedMart, I have engineered solutions that not only optimized operational costs and accuracy but also elevated user engagement by crafting seamless interfaces with React.js. I am particularly proud of my Python automation project that leveraged OpenAI API for data processing—an endeavor that reflects my aptitude for devising efficient, scalable solutions. Furthermore, my contributions to team projects, such as designing machine learning pipelines, underscore my ability to collaborate effectively towards innovative outcomes. Together with my penchant for high-quality coding practices and open-source collaboration, I am perfectly positioned to contribute to Stripe's mission of building pioneering infrastructure.

\end{cvletter}


%-------------------------------------------------------------------------------
% Print the signature and enclosures with above letter informations
\makeletterclosing

\end{document}
